Uncertainty propagation in deep neural networks for sparse coding

### 2018-03-09 paper/BayesianLISTA.tex
the first sentence corrected

\begin{abstract}
Bayesian neural networks impose prior distributions on weights of a network and infer a posterior distribution of an output, rather than a point prediction as in the conventional neural networks. Therefore, Bayesian neural networks estimate both an output for a test data and uncertainty of this prediction. Uncertainty of the prediction is a result of propagating weight uncertainty via layers of a network. We propose a method of propagating uncertainty through the soft-thresholding nonlinearity. The method expands the area of Bayesian neural networks and allows the soft-thresholding nonlinearity to be used in novel Bayesian sparse coding deep neural networks. As an example we design a Bayesian Learned Iterative Shrinkage-Thresdholding Algorithm (Bayesian \textsc{lista}) network. We develop a highly efficient posterior inference algorithm based on probabilistic backpropagation. A series of experiments show that the proposed framework provide both accurate predictions and reasonable estimates of uncertainty in these predictions.
\end{abstract}

>>>>

\begin{abstract}
In the Bayesian neural network framework prior distributions are imposed on weights of a network and a posterior distribution of an output is inferred, rather than a point prediction in the conventional neural networks. Therefore, Bayesian neural networks estimate both an output for a test data and uncertainty of this prediction. Uncertainty of the prediction is a result of propagating weight uncertainty via layers of a network. We propose a method of propagating uncertainty through the soft-thresholding nonlinearity. The method expands the area of Bayesian neural networks and allows the soft-thresholding nonlinearity to be used in novel Bayesian sparse coding deep neural networks. As an example we design a Bayesian Learned Iterative Shrinkage-Thresdholding Algorithm (Bayesian \textsc{lista}) network. We develop a highly efficient posterior inference algorithm based on probabilistic backpropagation. A series of experiments show that the proposed framework provide both accurate predictions and reasonable estimates of uncertainty in these predictions.
\end{abstract}
